Tom Stafford

### 2024-05-11 index.qmd
smalls

I Direct the MSc programmes in Psychological Research Methods, and set up the MSc in Psychological Research Methods with Data Science. I teach a module on [Data Management and Visualisation](https://tomstafford.github.io/psy6422/).

At the University I hold the position of Research Practice Lead, an institution-wide role with a remit to encourage practices which support robust and trusted research. As Research Practice Lead, I represent the University of Sheffield on the UK Reproducibility Network, and chair the national UKRN Institutional Leads group.

>>>>

I direct the MSc programmes in Psychological Research Methods, and set up the MSc in Psychological Research Methods with Data Science. I teach a module on [Data Management and Visualisation](https://tomstafford.github.io/psy6422/).

At the University I hold the position of Research Practice Lead, an institution-wide role with a remit to encourage practices which support robust and trusted research. As Research Practice Lead, I represent the University of Sheffield on the [UK Reproducibility Network](https://www.ukrn.org/), for which I chair the national [UKRN Institutional Leads group](https://www.ukrn.org/institutional-leads/).
